Biden Predicted to Secure a Minimum 10% Lead in Popular Votes Over Trump in the 2024 Election

### 2024-03-11 outputs/paper.qmd
add references and modify download script

---
title: "Joe Biden won popular votes in 2024 US Presidential Election"
format: pdf
date: "9 March 2024"
date-format: "D MMMM YYYY"
number-sections: true
thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/2024prediction_USPresidentialElection"
toc: true

---
```{r}
#| include: false
library(dplyr)
library(ggplot2)
library(knitr)
library(statebins)
library(modelsummary)
library(broom)
library(readr)
library(here)
library(kableExtra)
library(arrow)
```

@@

>>>>

---
title: "Biden Predicted to Secure a Minimum 10% Lead in Popular Votes Over Trump in the 2024 Election"
author: 
  - Boxuan Yi
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: ""
date: "10 March 2024"
date-format: "D MMMM YYYY"
number-sections: true
thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/2024prediction_USPresidentialElection"
toc: true
bibliography: references.bib
---
```{r}
#| include: false
library(dplyr)
library(ggplot2)
library(knitr)
library(statebins)
library(modelsummary)
library(broom)
library(readr)
library(here)
library(kableExtra)
library(arrow)
```

@@

\newpage
